%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\sub}[2]{%
\par\noindent\begin{tabular*}{0.97\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
\textit{\small #1} & \textit{\small #2} \
\end{tabular*}\par\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{marwahoualla.com}{\Large Marwa Houalla}} &\href{mailto:mhoualla@umich.edu}{mhoualla@umich.edu}\\
  \href{http://mhoualla.com/}{http://www.mhoualla.com} &\href{}{Washington DC-Baltimore Metropolitan Area} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Michigan}{Ann Arbor, Michigan}
      {Honors Bachelor of Science in Computer Science;  GPA: 3.9}{Sep 2020 - Dec 2023}
      \sub{Relevant Coursework: Advanced Operating Systems, Web Systems, UI/UX Design, Compiler Construction}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Wayfair}{Boston, MA}
      {Incoming Software Development Engineer Intern}{June 2023 - Present }

% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {University of Michigan EECS}{Ann Arbor, MI}
      {Teaching Assistant for Data Structures \& Algorithms}{Dec 2021 - Present}
      \resumeItemListStart
        \resumeItem{}{Help professors teach 900+ students per semester algorithm analysis, O-notation, fundamental data structures (stacks, queues, deques and hash tables), and algorithm techniques (dynamic programming, greedy, recursive, divide-and-conquer, branch-and-bound, and backtracking). }
        \resumeItem{}{Lead a weekly lab section, ideate and write exam questions, answer conceptual questions on Piazza.}
        \resumeItem{}{Hold weekly office hours for debugging and optimizing projects containing more than 1000 lines of code.}
        \resumeItemListEnd
      \sub{Grader for Introduction to Computer Architecture}{Sep 2022 - Present}
      \resumeItemListStart
      \resumeItem{}{Grade assignments and exams on computer organization topics, such as caches, virtual memory, multi- and single-cycle datapaths, pipelining, and information set architecture.}
      \resumeItemListEnd

    \resumeSubheading
      {T. Rowe Price}{New York, NY}
      {Software Engineer Intern}{June 2022 - Sep 2022}
      \resumeItemListStart
      \resumeItem{}{Built Grafana dashboards with proper metrics using Prometheus, Telegraf, Splunk, and Cloudwatch for the Enterprise HashiCorp Vault application.}
      \resumeItem{}{Implemented an alerting system with Alertmanager to proactively be notified of Vault incidents.}
      \resumeItem{}{Integrated Sourcegraph code intelligence into the Gitlab UI using Docker.}
      \resumeItem{}{Collected firmwide VDI information using Prometheus and broke it out by geolocation to better understand update and consumption patterns.}
      \resumeItemListEnd

    \resumeSubheading{Ford School of Public Policy}{Ann Arbor, MI}{Researcher}{Sep 2020 - Present}
    \resumeItemListStart
    \resumeItem{}{Experimental research on hiring discrimination under the supervision of Professor Fabiana Silva.}
    \resumeItem{}{Assist in designing and testing experimental stimuli, edit manuscripts, code MTurk survey responses, and conduct several literature reviews.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Thread Library (C++17):}
      {Implemented sophisticated Thread Library to handle the creation, execution, and lifespan of multiple thread bodies on a multi-core architecture, equipped with advanced functionalities such as conditional variables, mutexes, generic threads, inner process interrupt capabilities, and thread lifetime management operations including yield and join.}
    \resumeSubItem{Virtual Memory Manager (C++17):}
      {Designed and implemented virtual memory manager that supports file- and swap-backed pages, maintaining processes' address spaces via the pager interface, enabling syscalls, forking of child processes with non-empty virtual arena, and creating customizable memory sizes with a clock queue to control eviction orders and enable bits for read, write permissions and physical page residency.}
    \resumeSubItem{LinkedIn Data Scraper and Classification Tool (Python 3):}{Created suite of scripts to extract recommendation data from LinkedIn profiles, facilitating in-depth textual analysis of the collected data using a Naive Bayes classifier and the Scikit-learn Python framework. Analyzed gender-associated words as part of an Honors Thesis, achieving the highest ranking for this project.}
    \resumeSubItem{Network Fileserver (C++17)}
      {Designed and implemented a multi-threaded network file server with fine-grained locking, socket programming, client-server systems, and network protocols.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------

%--------PROGRAMMING SKILLS------------
\section{Skills}
      \textbf{Languages}{: C++, C, Rust, Python, Javascript, HTML, CSS, GDB} \break
      \textbf{Technologies}{: AWS, React, Grafana, Figma} \break
      \textbf{OS}{: Arch Linux, MacOS, Windows}

\end{document}
